Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-07-22 chap-intro.tex
Refine

\Cref{part:incr} is originally based on work by \citet*{CaiEtAl2014ILC}, though
significantly revised; only \cref{sec:applying} survives mostly unchanged.
This work was even more of a team effort. I designed the
overall project and came up with the original notion of change structures; Cai
Yufei contributed differentiation itself and its first correctness proof.
\Cref{part:incr} contains novel correctness proof; its history and
contributions are discussed in \cref{sec:ilc-dev-history}.

>>>>

The first chapters \cref{part:incr} is originally based on work by \citet*{CaiEtAl2014ILC}, though
significantly revised; only \cref{sec:applying,sec:rw} survives mostly unchanged.
This work was even more of a team effort. I designed the
overall project and came up with the original notion of change structures; Cai
Yufei contributed differentiation itself and its first correctness proof.
\Cref{part:incr} contains novel correctness proof; its history and
contributions are discussed in \cref{sec:ilc-dev-history}.
